\documentclass[11pt, letterpaper]{article}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[margin=1in, top=0.85in, bottom=0.85in]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{mdframed}
\usepackage{hyperref}
\usepackage{amssymb}

% ── Colors ────────────────────────────────────────────────────────────────────
\definecolor{deepgreen}{RGB}{34, 85, 48}
\definecolor{lightgreen}{RGB}{224, 240, 228}
\definecolor{stone}{RGB}{245, 243, 238}
\definecolor{darkgray}{RGB}{50, 50, 50}
\definecolor{midgray}{RGB}{110, 110, 110}
\definecolor{accent}{RGB}{87, 143, 72}

% ── Section styling ───────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{black}}{}{0em}{}[\color{accent}\titlerule]
\titlespacing{\section}{0pt}{16pt}{6pt}

\titleformat{\subsection}
  {\normalsize\bfseries\color{darkgray}}{}{0em}{}
\titlespacing{\subsection}{0pt}{10pt}{3pt}

% ── Header / Footer ───────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{{\color{accent}\hrule height 0.4pt}}
\fancyhead[L]{\small\color{midgray}\textit{Follow-Up Questions --- Option A: Custom Build}}
\fancyhead[R]{\small\color{midgray}\textit{Ideal Landscape Services}}
\fancyfoot[C]{\small\color{midgray}\thepage}

% ── List styling ──────────────────────────────────────────────────────────────
\setlist[itemize]{noitemsep, topsep=3pt, leftmargin=1.4em}
\setlist[enumerate]{noitemsep, topsep=3pt, leftmargin=1.4em}

% ── Checklist environment ─────────────────────────────────────────────────────
\newlist{checklist}{itemize}{2}
\setlist[checklist,1]{label=$\square$, noitemsep, topsep=6pt, leftmargin=1.8em, itemsep=8pt}
\setlist[checklist,2]{label=$\circ$, noitemsep, topsep=2pt, leftmargin=1.4em, itemsep=1pt}

% ── Note box ──────────────────────────────────────────────────────────────────
\newmdenv[
  backgroundcolor=stone,
  linecolor=midgray,
  linewidth=0.6pt,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  roundcorner=4pt,
  skipabove=8pt,
  skipbelow=8pt
]{notebox}

% ── Hyperlink styling ─────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=deepgreen, linkcolor=deepgreen}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}
% ══════════════════════════════════════════════════════════════════════════════

% ── Title block ───────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{black} Follow-Up Questions}\\[4pt]
  {\large\color{darkgray} Ideal Landscape Services --- Option A: Custom Build}\\[6pt]
  {\small\color{midgray} React / Next.js + Firebase \quad·\quad March 2026 \quad·\quad Confidential}
\end{center}

\vspace{4pt}
{\color{accent}\hrule height 1.2pt}
\vspace{10pt}

These questions apply to the \textbf{Custom Build path (Option A)}: a fully
bespoke React/Next.js site with a Firebase backend and a custom \textbf{/admin
dashboard} you control without ever touching code or a third-party CMS.
WordPress-specific questions have been removed. Answers here directly unblock
the design, development, and launch phases.

\vspace{4pt}

% ══════════════════════════════════════════════════════════════════════════════
\section{Domain \& Email}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Who is the current domain registrar?}
    (GoDaddy, Namecheap, Google Domains, etc.)
    \begin{checklist}
      \item DNS access is needed at launch to point the domain to Firebase Hosting.
      \item MX records must \emph{not} change --- company email is completely
            unaffected by the site move.
    \end{checklist}

  \item \textbf{What email provider are the company emails on?}
    (Google Workspace, Microsoft 365, or bundled with the current WPEngine hosting?)
    \begin{checklist}
      \item If Google Workspace or M365: no action needed --- emails survive the transition.
      \item If bundled with WPEngine: email migration must happen \emph{before}
            WPEngine is canceled.
    \end{checklist}

  \item \textbf{How many active email accounts are there?}
    (e.g., kathy@, david@, info@, quotes@, etc.)
    \begin{checklist}
      \item Good to know if an email provider switch is ever needed.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Hosting \& Current Setup}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Who currently manages the WPEngine account --- David, or DRKM Strategies?}
    \begin{checklist}
      \item The WPEngine account should be canceled \emph{after} the new site is live,
            not before. The old site stays up as a reference during the build.
      \item You (or whoever holds the account) initiate the cancellation.
    \end{checklist}

  \item \textbf{Do you have a Google account to use for the Firebase project?}
    \begin{checklist}
      \item Firebase is tied to a Google/Gmail account. Any Google Workspace or
            Gmail account works.
      \item The project is set up under your account so you own the hosting,
            database, and storage outright.
      \item Firebase Hosting is free at this site's traffic level. No monthly bill.
    \end{checklist}

  \item \textbf{Do you want the existing 8 blog posts migrated to the new site?}
    \begin{checklist}
      \item All 8 posts have already been archived locally --- full text, dates,
            and slugs preserved. Nothing is at risk.
      \item If \textbf{yes}: posts will be reformatted and imported into the new
            blog system, with 301 redirects from the old URLs.
      \item If \textbf{no}: the blog launches fresh; new posts follow the SEO
            content plan.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Admin Dashboard Scope}
% ══════════════════════════════════════════════════════════════════════════════

The custom build includes a \textbf{/admin panel} protected by login where you
or Kathy can update site content in the browser --- no code, no FTP, no plugin
updates. The following are planned for admin control. Confirm or adjust:

\begin{checklist}
  \item \textbf{Blog posts} --- Add new posts with title, date, cover image, and body text.
    \begin{checklist}
      \item This is the primary use case and is confirmed in scope.
    \end{checklist}

  \item \textbf{Project / portfolio entries} --- Add new projects with a name, city,
        photos, and a brief description.
    \begin{checklist}
      \item Do you want this in the admin, or is updating projects a
            build-time task handled by the developer?
    \end{checklist}

  \item \textbf{Testimonials} --- Should the admin allow adding testimonials,
        or will the reviews section be powered entirely by the live Google review feed?

  \item \textbf{Gallery images} --- Should service page photos be swappable from
        the admin, or is a one-time load at launch acceptable?

  \item \textbf{Any other content you or Kathy frequently update?}
    (Seasonal promotions, pricing callouts, team bios, announcements, etc.)
\end{checklist}

\begin{notebox}
\small The admin panel is intentionally minimal --- it only exposes what you
actually need. More admin features = more build time = higher cost. Being
specific here keeps scope and budget tight.
\end{notebox}

% ══════════════════════════════════════════════════════════════════════════════
\section{Design \& Content}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Does Ideal have a professional photo library, or do new photos
        need to be taken?}
    \begin{checklist}
      \item The Miracle Farms aesthetic \emph{requires} hero-quality photography.
            This is the single most important factor in hitting that look.
      \item A professional photoshoot is worth budgeting for if the existing
            library doesn't have full-viewport-quality shots.
    \end{checklist}

  \item \textbf{Does Ideal have any named or featured projects?}
    \begin{checklist}
      \item Like Miracle Farms' ``Shoreland Overlook'' or ``Fernscape Modern.''
      \item Named projects become signature portfolio cards on the Projects page.
    \end{checklist}

  \item \textbf{Does Ideal have certifications, awards, trade memberships, or
        partner logos to display?}
    \begin{checklist}
      \item TNLA membership logo and Home \& Garden Show Award photos have already
            been found in the scraped image library and are ready to use.
      \item Any additional credentials? (BBB, NALP, contractor licensing seals, etc.)
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Features \& Functionality}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{What does the ``Pay Online'' button currently link to?}
    \begin{checklist}
      \item External payment portal (PayPal, QuickBooks Online, etc.) --- easy
            to replicate with a redirect link.
      \item Built-in payment processing on the new site --- significant added
            scope; will adjust the estimate.
    \end{checklist}

  \item \textbf{Do you want a live chat or text widget on the site?}
    \begin{checklist}
      \item Third-party embed (Tidio, JivoChat, etc.) --- low development effort,
            minimal monthly cost (~\$0--\$20/mo). Similar to what Worx uses.
    \end{checklist}

  \item \textbf{Do you have existing Google Analytics or Search Console data
        to transfer?}
    \begin{checklist}
      \item If yes: I'll need access to your Google account to transfer the GA4 property.
      \item If no existing property: new GA4 + Search Console will be set up from
            scratch at launch.
    \end{checklist}

  \item \textbf{Is the newsletter/email subscriber list currently active?}
    \begin{checklist}
      \item If yes: what platform? (Mailchimp, Constant Contact, etc.)
      \item The subscriber list must be exported \emph{before} WPEngine is canceled.
    \end{checklist}

  \item \textbf{Do you want live Google review integration?}
    \begin{checklist}
      \item Custom build option: Google Places API --- free at this traffic level,
            server-rendered in Next.js, no subscription needed.
      \item Widget alternative: EmbedSocial or Widewail (\$29--\$49/mo) with
            more display flexibility.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Scope \& Timeline}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Are there any hard deadlines?}
    (Busy season, upcoming marketing push, trade show, referral timeline, etc.)

  \item \textbf{Are there features or pages beyond the agreed 11-page plan?}
    \begin{checklist}
      \item Examples: online quote calculator, appointment scheduling, job listings,
            an e-commerce store, a client portal.
      \item Anything outside the 11-page scope is quoted separately.
    \end{checklist}

  \item \textbf{Will you write new copy, or would you like help trimming the
        existing copy to match the ``less words'' direction?}
    \begin{checklist}
      \item All existing service page copy, blog posts, FAQs, and testimonials
            have been archived locally --- the raw material is ready.
      \item Light copy editing to fit the visual-first style is included in scope.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Image Library \& Before/After}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Are the unidentified photos in the archive before/after shots or
        job-site documentation?}
    \begin{checklist}
      \item The \texttt{misc/} folder contains $\sim$99 dated photos (e.g.,
            \texttt{20170320\_105522...}) that appear to be field-taken.
      \item If confirmed as before/after: these become a
            \textbf{``Transformations''} feature section on the homepage ---
            one of the highest-engagement elements on a landscaping site,
            at no extra cost.
      \item If unidentified: excluded from the build.
    \end{checklist}

  \item \textbf{Can you name the unlabeled project photo sets?}
    \begin{checklist}
      \item Sets needing labels: P-series (12 photos), AR-series (2 photos), 8609.jpg.
      \item A project name and city/neighborhood is all that's needed to turn
            them into named portfolio cards.
    \end{checklist}

  \item \textbf{Are there more project photos on the WPEngine server that the
        scraper didn't capture?}
    \begin{checklist}
      \item The scraper only collected images referenced by live pages.
      \item WPEngine SFTP or the WordPress ``Export Media Library'' plugin may
            surface unpublished shoots or archived jobs.
      \item These should be retrieved \emph{before} WPEngine access is lost.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Design Decisions}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{What should the site's brand tagline be?}
    \begin{checklist}
      \item ``Design --- Build --- Maintain'' \quad (Miracle Farms-style, service-focused)
      \item ``Your Ideal Outdoors, Built.'' \quad (brand-specific, punchy)
      \item Something else?
    \end{checklist}
    \textit{\small This appears in the hero section and potentially in browser tab titles.}

  \item \textbf{After viewing the image library, are any existing photos
        hero-quality?}
    \begin{checklist}
      \item Hero = full-viewport, sharp at 1920px+ width.
      \item If not: a photoshoot before launch is the recommended path.
    \end{checklist}

  \item \textbf{Would you like to simplify navigation from 8 links to 6?}
    \begin{checklist}
      \item Proposed: Home $|$ Services $|$ Projects $|$ About $|$ Blog $|$ Contact
      \item FAQ folds into Services as an accordion section.
      \item Testimonials folds into About or the homepage reviews strip.
      \item Alternatively: keep Testimonials as a standalone page.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{SEO \& Reviews}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Does Ideal have a claimed and verified Google Business Profile?}
    \begin{checklist}
      \item If unclaimed: needs to be claimed before or during the build.
      \item The Name, Address, and Phone on the website must match GBP exactly.
    \end{checklist}

  \item \textbf{Are you open to live Google review integration?}
    \begin{checklist}
      \item Custom build approach: fetch via Google Places API --- free, server-rendered,
            no third-party subscription.
      \item Star rating + review count auto-update as new reviews come in.
    \end{checklist}

  \item \textbf{Which DFW cities and neighborhoods does Ideal currently serve?}
    \begin{checklist}
      \item Used for the Service Area section and optional city subpages.
      \item City subpages independently target local searches like
            ``landscape design in Allen TX'' --- low build effort, strong SEO return.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Business Info (NAP \& Contact)}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{What is the business's physical mailing address?}
    \begin{checklist}
      \item No address appears anywhere on the current site.
      \item Needed for LocalBusiness schema markup and GBP NAP consistency.
      \item If you prefer not to display it publicly, it can go in schema
            markup only --- invisible to visitors, readable by Google.
    \end{checklist}

  \item \textbf{Confirm: is (817) 457-7507 the correct primary phone number?}
    \begin{checklist}
      \item This number is used in the header, footer, CTA buttons, schema
            markup, and GBP listing.
    \end{checklist}

  \item \textbf{The current footer credits ``Designed by: DRKM Strategies.''
    Keep, remove, or replace on the new site?}

  \item \textbf{Do you know if/when DRKM Strategies plans to take the old
    site down?}
    \begin{checklist}
      \item All blog posts, FAQs, testimonials, service copy, and images have
            been archived --- nothing will be lost when the domain goes dark.
      \item A confirmed timeline helps prioritize what gets built first.
    \end{checklist}
\end{checklist}

\vspace{16pt}
{\color{accent}\hrule height 0.6pt}
\vspace{8pt}

\begin{center}
  \small\color{midgray}
  These answers directly unblock the next phase of the custom build.\\
  For the WordPress version of these questions, see \emph{followupWP}.
\end{center}

\end{document}
