\documentclass[11pt, letterpaper]{article}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[margin=1in, top=0.85in, bottom=0.85in]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{mdframed}
\usepackage{hyperref}
\usepackage{amssymb}

% ── Colors ────────────────────────────────────────────────────────────────────
\definecolor{deepgreen}{RGB}{34, 85, 48}
\definecolor{lightgreen}{RGB}{224, 240, 228}
\definecolor{stone}{RGB}{245, 243, 238}
\definecolor{darkgray}{RGB}{50, 50, 50}
\definecolor{midgray}{RGB}{110, 110, 110}
\definecolor{accent}{RGB}{87, 143, 72}

% ── Section styling ───────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{black}}{}{0em}{}[\color{accent}\titlerule]
\titlespacing{\section}{0pt}{16pt}{6pt}

\titleformat{\subsection}
  {\normalsize\bfseries\color{darkgray}}{}{0em}{}
\titlespacing{\subsection}{0pt}{10pt}{3pt}

% ── Header / Footer ───────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{{\color{accent}\hrule height 0.4pt}}
\fancyhead[L]{\small\color{midgray}\textit{Follow-Up Questions --- Option B: WordPress Build}}
\fancyhead[R]{\small\color{midgray}\textit{Ideal Landscape Services}}
\fancyfoot[C]{\small\color{midgray}\thepage}

% ── List styling ──────────────────────────────────────────────────────────────
\setlist[itemize]{noitemsep, topsep=3pt, leftmargin=1.4em}
\setlist[enumerate]{noitemsep, topsep=3pt, leftmargin=1.4em}

% ── Checklist environment ─────────────────────────────────────────────────────
\newlist{checklist}{itemize}{2}
\setlist[checklist,1]{label=$\square$, noitemsep, topsep=6pt, leftmargin=1.8em, itemsep=8pt}
\setlist[checklist,2]{label=$\circ$, noitemsep, topsep=2pt, leftmargin=1.4em, itemsep=1pt}

% ── Note box ──────────────────────────────────────────────────────────────────
\newmdenv[
  backgroundcolor=stone,
  linecolor=midgray,
  linewidth=0.6pt,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  roundcorner=4pt,
  skipabove=8pt,
  skipbelow=8pt
]{notebox}

% ── Hyperlink styling ─────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=deepgreen, linkcolor=deepgreen}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}
% ══════════════════════════════════════════════════════════════════════════════

% ── Title block ───────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{black} Follow-Up Questions}\\[4pt]
  {\large\color{darkgray} Ideal Landscape Services --- Option B: WordPress Build}\\[6pt]
  {\small\color{midgray} WordPress + Elementor + SiteGround/Bluehost \quad·\quad March 2026 \quad·\quad Confidential}
\end{center}

\vspace{4pt}
{\color{accent}\hrule height 1.2pt}
\vspace{10pt}

These questions apply to the \textbf{WordPress Build path (Option B)}: an
11-page site built on WordPress with the Elementor page builder, a pre-configured
plugin stack, and managed hosting on SiteGround or Bluehost. Custom-build-specific
questions (admin dashboards, Firebase, etc.) have been removed. Answers here
directly unblock design, development, and launch planning.

\vspace{4pt}

% ══════════════════════════════════════════════════════════════════════════════
\section{Domain \& Email}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Who is the current domain registrar?}
    (GoDaddy, Namecheap, Google Domains, etc.)
    \begin{checklist}
      \item DNS access is needed at launch to point the domain to the new host.
      \item MX records must \emph{not} change --- company email is completely
            unaffected by the site move.
    \end{checklist}

  \item \textbf{What email provider are the company emails on?}
    (Google Workspace, Microsoft 365, or bundled with the current WPEngine hosting?)
    \begin{checklist}
      \item If Google Workspace or M365: no action needed --- emails survive the transition.
      \item If bundled with WPEngine: email migration must happen \emph{before}
            WPEngine is canceled.
    \end{checklist}

  \item \textbf{How many active email accounts are there?}
    (e.g., kathy@, david@, info@, quotes@, etc.)
    \begin{checklist}
      \item Important if email is bundled with WPEngine and needs to be migrated
            to the new host or a standalone provider.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Hosting \& Current Setup}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Who currently manages the WPEngine account --- David, or DRKM Strategies?}
    \begin{checklist}
      \item The WPEngine account should be canceled \emph{after} the new site is
            fully live and DNS has transferred. Do not cancel early.
      \item For a WP-to-WP move, a content export from the WPEngine dashboard
            may be needed --- this is easier if you have access.
    \end{checklist}

  \item \textbf{Do you have login access to the current WordPress admin?}
    (\texttt{ideallandscapeservices.com/wp-admin})
    \begin{checklist}
      \item WP admin access allows a clean XML export of all posts and pages,
            which can be imported directly into the new WordPress install.
      \item If you don't have access: all content has already been archived
            locally via the scraper --- nothing would be lost.
    \end{checklist}

  \item \textbf{Do you want existing blog posts and page content migrated,
        or start fresh?}
    \begin{checklist}
      \item \textbf{Migrate}: existing posts are imported via WP XML export and
            301-redirected from old URLs. Old SEO position is preserved.
      \item \textbf{Fresh start}: new posts written from the SEO content plan;
            old URLs redirected to the homepage or the blog index.
      \item All 8 blog posts and all page copy have been archived locally
            either way --- nothing is lost.
    \end{checklist}

  \item \textbf{Hosting preference for the new site?}
    \begin{checklist}
      \item \textbf{SiteGround} (\textasciitilde\$3.99--\$6.99/mo) --- faster
            servers, built-in caching (SuperCacher), free SSL, strong WordPress
            support. Recommended.
      \item \textbf{Bluehost} (\textasciitilde\$2.75--\$5.45/mo) --- widely used,
            slightly cheaper, slightly slower. Officially recommended by WordPress.org.
      \item \textbf{Stay on WPEngine} (\textasciitilde\$25+/mo) --- premium managed
            WP hosting; worth it for large traffic, unnecessary for this site's scale.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{WordPress Content Management}
% ══════════════════════════════════════════════════════════════════════════════

The WordPress admin panel is the built-in CMS --- no custom development needed.
The following questions shape how the site is configured so David and Kathy can
manage it with minimal friction:

\begin{checklist}
  \item \textbf{Are you (or Kathy) comfortable with the WordPress admin panel?}
    \begin{checklist}
      \item WordPress familiarity varies widely. The site will be pre-configured
            with the right plugins and permissions, but day-to-day editing assumes
            basic WP comfort.
      \item A short walkthrough session at handoff is included in scope.
    \end{checklist}

  \item \textbf{Who will primarily update the site after launch --- you, Kathy,
        or will updates be requested from me?}
    \begin{checklist}
      \item This determines which user roles and permissions to set up.
      \item Kathy may be better suited for routine updates (blog posts, photo swaps)
            given her office manager role --- but your preference takes priority.
    \end{checklist}

  \item \textbf{Are there content sections that should be \emph{locked} to
        prevent accidental changes?}
    \begin{checklist}
      \item Example: homepage hero design locked; only blog/testimonials editable.
      \item Elementor allows granular template locking per user role.
    \end{checklist}

  \item \textbf{Any preference on the contact form setup?}
    \begin{checklist}
      \item Default plan: WPForms or Gravity Forms --- quote request form with
            Name, Phone, Email, Service, Message, and a file upload for reference photos.
      \item Form submissions can go to any email address(es). Confirm who should
            receive them: David, Kathy, both?
    \end{checklist}
\end{checklist}

\begin{notebox}
\small The full plugin stack is pre-configured and included in the flat fee:
Elementor Pro (page builder), Yoast SEO, WPForms, Smush (images), Wordfence
(security), UpdraftPlus (automated backups), WP Rocket or SiteGround Optimizer
(caching), and Site Kit by Google (GA4 + Search Console). No plugin subscription
costs are passed on --- Ideal Landscape Services is responsible for hosting
and domain as ongoing costs.
\end{notebox}

% ══════════════════════════════════════════════════════════════════════════════
\section{Design \& Content}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Does Ideal have a professional photo library, or do new photos
        need to be taken?}
    \begin{checklist}
      \item The Miracle Farms aesthetic \emph{requires} hero-quality photography.
            This is the single most important factor in hitting that look.
      \item A professional photoshoot is worth budgeting for if the existing
            library doesn't have full-viewport-quality shots.
    \end{checklist}

  \item \textbf{Does Ideal have any named or featured projects?}
    \begin{checklist}
      \item Like Miracle Farms' ``Shoreland Overlook'' or ``Fernscape Modern.''
      \item Named projects become signature portfolio cards on the Projects page.
    \end{checklist}

  \item \textbf{Does Ideal have certifications, awards, trade memberships, or
        partner logos to display?}
    \begin{checklist}
      \item TNLA membership logo and Home \& Garden Show Award photos have already
            been found in the scraped image library and are ready to use.
      \item Any additional credentials? (BBB, NALP, contractor licensing seals, etc.)
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Features \& Functionality}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{What does the ``Pay Online'' button currently link to?}
    \begin{checklist}
      \item External portal (PayPal, QuickBooks Online, etc.) --- easy redirect link.
      \item Built-in WooCommerce payment processing --- significant added scope;
            will adjust the estimate.
    \end{checklist}

  \item \textbf{Do you want a live chat or text widget on the site?}
    \begin{checklist}
      \item Third-party embed (Tidio, JivoChat, etc.) --- a simple embed snippet
            in the WordPress footer, no development effort. Similar to Worx.
    \end{checklist}

  \item \textbf{Do you have existing Google Analytics or Search Console data
        to transfer?}
    \begin{checklist}
      \item If yes: I'll need access to your Google account to transfer the GA4 property.
      \item Site Kit by Google plugin connects both GA4 and Search Console
            directly from the WP dashboard after setup.
    \end{checklist}

  \item \textbf{Is the newsletter/email subscriber list currently active?}
    \begin{checklist}
      \item If yes: what platform? (Mailchimp, Constant Contact, etc.)
      \item The subscriber list must be exported \emph{before} WPEngine is canceled.
      \item A Mailchimp or Constant Contact integration plugin can be added to the
            new site's footer form at no extra build cost.
    \end{checklist}

  \item \textbf{Do you want live Google review integration?}
    \begin{checklist}
      \item WordPress options: EmbedSocial widget (\$29--\$49/mo), Widewail
            (\$30--\$60/mo), WP Business Reviews plugin (\$49/yr), or Elfsight
            (free tier available).
      \item Alternative: manually curated testimonials via the Testimonials page
            --- zero ongoing cost, but requires manual updates.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Scope \& Timeline}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Are there any hard deadlines?}
    (Busy season, upcoming marketing push, trade show, referral timeline, etc.)

  \item \textbf{Are there features or pages beyond the agreed 11-page plan?}
    \begin{checklist}
      \item Examples: online quote calculator, appointment scheduling, job listings,
            a WooCommerce store, a client login portal.
      \item Anything outside the 11-page scope is quoted separately.
    \end{checklist}

  \item \textbf{Will you write new copy, or would you like help trimming the
        existing copy to match the ``less words'' direction?}
    \begin{checklist}
      \item All existing service page copy, blog posts, FAQs, and testimonials
            have been archived locally --- the raw material is ready.
      \item Light copy editing to fit the visual-first style is included in scope.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Image Library \& Before/After}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Are the unidentified photos in the archive before/after shots or
        job-site documentation?}
    \begin{checklist}
      \item The \texttt{misc/} folder contains $\sim$99 dated photos (e.g.,
            \texttt{20170320\_105522...}) that appear to be field-taken.
      \item If confirmed as before/after: these become a \textbf{``Transformations''}
            feature section on the homepage --- at no extra cost.
      \item If unidentified: excluded from the build.
    \end{checklist}

  \item \textbf{Can you name the unlabeled project photo sets?}
    \begin{checklist}
      \item Sets needing labels: P-series (12 photos), AR-series (2 photos), 8609.jpg.
      \item A project name and city/neighborhood is all that's needed to turn
            them into named portfolio cards.
    \end{checklist}

  \item \textbf{Are there more project photos on the WPEngine server that the
        scraper didn't capture?}
    \begin{checklist}
      \item The scraper only collected images referenced by live pages.
      \item WPEngine SFTP or the WordPress ``Export Media Library'' plugin may
            surface unpublished shoots or archived jobs.
      \item These should be retrieved \emph{before} WPEngine access is lost.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Design Decisions}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{What should the site's brand tagline be?}
    \begin{checklist}
      \item ``Design --- Build --- Maintain'' \quad (Miracle Farms-style, service-focused)
      \item ``Your Ideal Outdoors, Built.'' \quad (brand-specific, punchy)
      \item Something else?
    \end{checklist}
    \textit{\small This appears in the hero section and in the browser tab title.}

  \item \textbf{After viewing the image library, are any existing photos
        hero-quality?}
    \begin{checklist}
      \item Hero = full-viewport, sharp at 1920px+ width.
      \item If not: a photoshoot before launch is the recommended path.
    \end{checklist}

  \item \textbf{Would you like to simplify navigation from 8 links to 6?}
    \begin{checklist}
      \item Proposed: Home $|$ Services $|$ Projects $|$ About $|$ Blog $|$ Contact
      \item FAQ folds into Services as an Elementor accordion section.
      \item Testimonials folds into About or the homepage reviews strip.
      \item Alternatively: keep Testimonials as a standalone page.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{SEO \& Reviews}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{Does Ideal have a claimed and verified Google Business Profile?}
    \begin{checklist}
      \item If unclaimed: needs to be claimed before or during the build.
      \item NAP (Name, Address, Phone) on the site must match GBP exactly.
      \item Yoast SEO will generate the LocalBusiness schema automatically
            once the address and phone are entered in settings.
    \end{checklist}

  \item \textbf{Are you open to live Google review integration?}
    \begin{checklist}
      \item WordPress options: EmbedSocial, Widewail, Elfsight (free tier),
            or WP Business Reviews plugin (\$49/yr one-time).
      \item Reviews auto-update as new Google reviews come in --- no manual
            maintenance.
    \end{checklist}

  \item \textbf{Which DFW cities and neighborhoods does Ideal currently serve?}
    \begin{checklist}
      \item Used for the Service Area section and optional city subpages.
      \item Each city subpage independently targets local searches like
            ``landscape design in Allen TX.''
      \item In WordPress, city subpages are standard pages built with the
            same Elementor template --- minimal extra effort.
    \end{checklist}
\end{checklist}

% ══════════════════════════════════════════════════════════════════════════════
\section{Business Info (NAP \& Contact)}
% ══════════════════════════════════════════════════════════════════════════════

\begin{checklist}
  \item \textbf{What is the business's physical mailing address?}
    \begin{checklist}
      \item No address appears anywhere on the current site.
      \item Needed for LocalBusiness schema (generated by Yoast) and GBP NAP
            consistency.
      \item If you prefer not to display it publicly, it can go into Yoast's
            schema settings only --- invisible to visitors, readable by Google.
    \end{checklist}

  \item \textbf{Confirm: is (817) 457-7507 the correct primary phone number?}
    \begin{checklist}
      \item Used in the header, footer, CTA buttons, Yoast schema, and GBP.
    \end{checklist}

  \item \textbf{The current footer credits ``Designed by: DRKM Strategies.''
    Keep, remove, or replace on the new site?}

  \item \textbf{Do you know if/when DRKM Strategies plans to take the old
    site down?}
    \begin{checklist}
      \item All blog posts, FAQs, testimonials, service copy, and images have
            been archived --- nothing will be lost when the domain goes dark.
      \item A confirmed timeline helps prioritize what gets built first.
    \end{checklist}
\end{checklist}

\vspace{16pt}
{\color{accent}\hrule height 0.6pt}
\vspace{8pt}

\begin{center}
  \small\color{midgray}
  These answers directly unblock the next phase of the WordPress build.\\
  For the custom build version of these questions, see \emph{followupCustom}.
\end{center}

\end{document}
