\documentclass[11pt, letterpaper]{article}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[margin=1in, top=0.85in, bottom=0.85in]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{mdframed}
\usepackage{hyperref}
\usepackage{multicol}

% ── Colors ────────────────────────────────────────────────────────────────────
\definecolor{deepgreen}{RGB}{34, 85, 48}
\definecolor{lightgreen}{RGB}{224, 240, 228}
\definecolor{stone}{RGB}{245, 243, 238}
\definecolor{darkgray}{RGB}{50, 50, 50}
\definecolor{midgray}{RGB}{110, 110, 110}
\definecolor{accent}{RGB}{87, 143, 72}

% ── Section styling ───────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{black}}{}{0em}{}[\color{accent}\titlerule]
\titlespacing{\section}{0pt}{16pt}{6pt}

\titleformat{\subsection}
  {\normalsize\bfseries\color{darkgray}}{}{0em}{}
\titlespacing{\subsection}{0pt}{10pt}{3pt}

% ── Header / Footer ───────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\color{accent}\hrule height 0.4pt}
\fancyhead[L]{\small\color{midgray}\textit{Website Rebuild Proposal}}
\fancyhead[R]{\small\color{midgray}\textit{Ideal Landscape Services}}
\fancyfoot[C]{\small\color{midgray}\thepage}

% ── List styling ──────────────────────────────────────────────────────────────
\setlist[itemize]{noitemsep, topsep=3pt, leftmargin=1.4em}
\setlist[enumerate]{noitemsep, topsep=3pt, leftmargin=1.4em}

% ── Highlight box ─────────────────────────────────────────────────────────────
\newmdenv[
  backgroundcolor=lightgreen,
  linecolor=accent,
  linewidth=1pt,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  roundcorner=4pt,
  skipabove=8pt,
  skipbelow=8pt
]{highlight}

\newmdenv[
  backgroundcolor=stone,
  linecolor=midgray,
  linewidth=0.6pt,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  roundcorner=4pt,
  skipabove=8pt,
  skipbelow=8pt
]{notebox}

% ── Hyperlink styling ─────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=deepgreen,
  linkcolor=deepgreen
}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}
% ══════════════════════════════════════════════════════════════════════════════

% ── Title block ───────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{black} Website Rebuild Proposal}\\[4pt]
  {\large\color{darkgray} Ideal Landscape Services}\\[6pt]
  {\small\color{midgray} Prepared March 2026 \quad·\quad Confidential}
\end{center}

\vspace{4pt}
{\color{accent}\hrule height 1.2pt}
\vspace{12pt}

% ── Intro paragraph ───────────────────────────────────────────────────────────
This proposal outlines a full rebuild of \textbf{ideallandscapeservices.com},
designed around your brief: \emph{more aesthetics, less words.} The new site
will be photography-forward, fast, and built to rank on Google---without
keyword stuffing. Two build options are detailed below. Everything else
(design direction, content plan, SEO strategy) is the same regardless of
which path you choose.

% ══════════════════════════════════════════════════════════════════════════════
\section{Design Direction}
% ══════════════════════════════════════════════════════════════════════════════

The new site draws from two references you provided:

\begin{itemize}
  \item \textbf{Miracle Farms} (Kathy's pick) --- photography-first, editorial
        layout. Large hero images, minimal text, white space that signals quality.
  \item \textbf{Worx Landscaping} (David's pick) --- smart trust signals, a
        numbered process section, and live Google reviews.
\end{itemize}

\subsection*{What the new site will look like}

\begin{itemize}
  \item \textbf{Hero:} Full-viewport landscape photo + a 4--5 word headline.
        No paragraph text above the fold. Two CTA buttons: \emph{See Our Work}
        and \emph{Free Estimate.}
  \item \textbf{Services:} Icon tile grid linking to subpages---no descriptions
        on the homepage. Photos do the talking.
  \item \textbf{Portfolio:} Named project cards (like Miracle Farms' project
        galleries)---your best jobs become showcase features, not a generic grid.
  \item \textbf{Process:} Numbered steps---\emph{Call $\to$ Consult $\to$
        Design $\to$ Approve $\to$ Build $\to$ Enjoy.}
  \item \textbf{Trust signals:} ``35$+$ Years in DFW'' badge, credentials/award
        logos (TNLA, Home \& Garden Show Awards), 3-column ``Why Choose Us'' strip.
  \item \textbf{Reviews:} Live Google review feed---auto-updated, star-rated, no
        hardcoded quotes that go stale.
  \item \textbf{Service area:} Map section with city links---handles local SEO
        without body copy stuffing.
  \item \textbf{Copy budget:} 1 headline $+$ 1--2 sentences per section.
        Everything else is visual.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\section{Pages Included}
% ══════════════════════════════════════════════════════════════════════════════

\begin{multicols}{2}
\begin{itemize}
  \item Homepage (full layout above)
  \item Landscape Design \& Plants
  \item Water Features
  \item Hardscapes \& Patios
  \item Outdoor Living \& Pergolas
  \item Landscape Lighting
  \item Maintenance \& Irrigation
  \item Projects / Portfolio
  \item About
  \item Blog (template + setup)
  \item Contact
\end{itemize}
\end{multicols}

\vspace{-4pt}
\begin{notebox}
\small A Before \& After / Transformations section is included in the scope
\emph{pending confirmation} that the archived job-site photos are before/after
shots. If confirmed, this becomes a homepage feature at no extra cost.
\end{notebox}

% ══════════════════════════════════════════════════════════════════════════════
\section{SEO Strategy (Visual-First, No Stuffing)}
% ══════════════════════════════════════════════════════════════════════════════

Google's current ranking signals reward structure and relevance---not repeated
copy. Here's how the new site earns its rankings:

\begin{itemize}
  \item \textbf{Image alt text} --- Every photo (400$+$ images) gets a
        descriptive alt tag mentioning the subject and a DFW city name naturally.
        This is the biggest quick win for a photo-heavy site.
  \item \textbf{Page structure} --- Unique H1 per page, H2/H3 hierarchy, and
        semantic HTML so crawlers understand the content without needing walls
        of text.
  \item \textbf{Meta titles \& descriptions} --- Unique, keyword-rich title and
        description for every page---these also appear as ad copy in search results.
  \item \textbf{Service area section} --- City names (Dallas, Fort Worth, Allen,
        Plano, Frisco, etc.) as visible text and links; optional thin city subpages
        for high-value local keyword targeting.
  \item \textbf{Google Business Profile} --- NAP (name, address, phone) on the
        site matched exactly to GBP; photos uploaded directly; review count grows
        the local pack ranking.
  \item \textbf{Blog} --- Seasonal, targeted posts (\emph{``Best Plants for DFW
        Summers,''} \emph{``How Much Does a Water Feature Cost in Dallas?''}) keep
        building long-tail authority over time---completely separate from service
        page copy.
  \item \textbf{Technical:} XML sitemap, schema markup (LocalBusiness), Core
        Web Vitals optimization, 301 redirects from old URLs, GA4 + Search Console.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\section{Build Options}
% ══════════════════════════════════════════════════════════════════════════════

\vspace{6pt}

% ── Option 1 box ──────────────────────────────────────────────────────────────
\begin{highlight}
\textbf{\color{black}\large Option A --- Custom Build \hfill
\normalsize\$1,800--\$2,500 flat}

\vspace{4pt}
\textbf{Stack:} React / Next.js frontend $\cdot$ Firebase (database, image
storage, authentication) $\cdot$ Firebase Hosting $\cdot$ GitHub CI/CD
auto-deploy on every save.

\vspace{4pt}
\textbf{What's included:}
\begin{itemize}
  \item Full 11-page site built to the design direction above
  \item Custom \textbf{/admin dashboard} for you---add blog posts, swap
        gallery images, and edit testimonials directly in the browser.
        No third-party CMS subscription, no plugin updates, no learning curve
        beyond a simple form.
  \item Firebase Auth login protecting the admin area
  \item GitHub Actions CI/CD: push a change $\to$ site updates automatically
  \item Live Google review integration
  \item Before \& After section (if photos confirmed)
  \item City subpages for local SEO (up to 10 cities)
  \item Full SEO setup: alt text, meta tags, schema, sitemap, GA4
  \item Mobile-responsive across all screen sizes
\end{itemize}

\vspace{4pt}
\textbf{Timeline:} 3--4 months part-time \quad
\textbf{Your annual cost after launch:} \textasciitilde\$15/yr (domain only)
\end{highlight}

\vspace{8pt}

% ── Option 2 box ──────────────────────────────────────────────────────────────
\begin{mdframed}[
  backgroundcolor=stone,
  linecolor=midgray,
  linewidth=0.6pt,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  roundcorner=4pt
]
\textbf{\color{darkgray}\large Option B --- WordPress Build \hfill
\normalsize\$960--\$1,440 flat}

\vspace{4pt}
\textbf{Stack:} WordPress $\cdot$ Elementor page builder $\cdot$ Hello
Elementor theme (custom child theme) $\cdot$ SiteGround or Bluehost managed
hosting.

\vspace{4pt}
\textbf{What's included:}
\begin{itemize}
  \item Full 11-page site built to the design direction above
  \item \textbf{WordPress admin panel} for you---the familiar interface most
        small-business owners already know. Add posts, update images, and edit
        pages without any help.
  \item Plugin stack pre-configured: contact forms, gallery, SEO (Yoast),
        security (Wordfence), caching, image compression, automated backups
  \item Live Google review integration
  \item Before \& After section (if photos confirmed)
  \item City subpages for local SEO (up to 10 cities)
  \item Full SEO setup: alt text, meta tags, schema, sitemap, GA4
  \item Mobile-responsive across all screen sizes
\end{itemize}

\vspace{4pt}
\textbf{Timeline:} 6--8 weeks part-time \quad
\textbf{Your annual cost after launch:} \textasciitilde\$115--\$215/yr
(hosting $+$ domain)
\end{mdframed}

\vspace{10pt}

% ── Side-by-side comparison table ─────────────────────────────────────────────
\begin{tabularx}{\linewidth}{lXX}
\toprule
 & \textbf{Option A --- Custom} & \textbf{Option B --- WordPress} \\
\midrule
Flat fee             & \$1,800--\$2,500        & \$960--\$1,440 \\
Timeline             & 3--4 months             & 6--8 weeks \\
You update the site  & Custom admin panel      & WP admin (familiar) \\
Annual cost          & \textasciitilde\$15/yr  & \textasciitilde\$115--\$215/yr \\
Long-term maintenance & Very low               & Moderate (plugin updates) \\
Platform lock-in     & None --- fully portable & WordPress ecosystem \\
\bottomrule
\end{tabularx}

% ══════════════════════════════════════════════════════════════════════════════
\section{Pricing \& What's Not Included}
% ══════════════════════════════════════════════════════════════════════════════

Both flat fees are priced at \$20/hr---well below the junior freelance market
rate of \$35--\$50/hr. Freelancers typically charge \$2,500--\$6,000 for a
WordPress rebuild of this scope; agencies charge \$8,000--\$20,000$+$.

\textbf{The flat fee covers} everything listed above. Ideal Landscape Services is responsible for
domain and hosting costs on top of the flat fee.

\textbf{Not included in flat fee:}
\begin{itemize}
  \item Professional photoshoot (recommended if hero images need upgrading)
  \item Third-party review platform subscription (NiceJob, EmbedSocial, etc.
        --- typically \$29--\$79/mo; free embeds are available as an alternative)
  \item Ongoing maintenance retainer (optional --- \$25--\$60/mo depending on
        option; covers updates, backups, and minor content changes)
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\section{Before We Start}
% ══════════════════════════════════════════════════════════════════════════════

A few quick answers from you will unblock the build immediately:

\begin{enumerate}
  \item \textbf{Which option?} Custom (A) or WordPress (B)?
  \item \textbf{Archived photos:} The ~99 unidentified photos in the image
        library---are those before/after or job-site progress shots?
  \item \textbf{Project names:} Can you provide names for the unlabeled
        project photo sets so they become named portfolio cards?
  \item \textbf{Hero photo quality:} Are any of the existing photos
        high-resolution enough for a full-viewport hero, or should we
        plan a photoshoot?
  \item \textbf{Service cities:} Which DFW cities/neighborhoods should be
        listed in the service area section?
\end{enumerate}

\vspace{12pt}
{\color{accent}\hrule height 0.6pt}
\vspace{8pt}

\begin{center}
  \small\color{midgray}
  Questions? Reach out anytime.\\
  This proposal is valid for 60 days from the date above.
\end{center}

\end{document}
